---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RMeasley)
```

```{r}
plot_gdp_cases_map(measles_data, year_chosen = 2024, top_n = 20)
```

This will create a map using leaflet showing the top n countries with the highest gdp per capita and lowest measles case count per 1,000,000 people in the population in a specified year. There will be different colored markers for the gdp category and measles category, and a separate color for countries that fall in both categories. The default year is 2024 and the default top n is 20.

```{r}
measles_incidence_rates_gdp(measles_data, region = "Africa", year)
```

This will produce a summary output of average measles incidence rate for a given region for 5 GDP groups in a specified year. The GDP groups are determined as quintiles of GDP values in that year. The default region is Africa and the default year is 2024.

```{r}
epi_linked_cases(measles_data, region = "Africa")
```

This will produce a summary output of the proportion of measles cases that are epidemiologically linked for a specified region in all years. The default region is Africa.

